Hello OpenScPCA

### 2024-04-02 analyses/hello-R/hello.Rmd

```{r}
count_sce <- function(sce_file) {
  # function to count cells in an sce file
  # returns a data frame with the following columns:
  # - project_id
  # - sample_id
  # - library_id
  # - n_cells: number of cells in the library

@@

## Session Info

>>>>

```{r}
count_sce <- function(sce_file) {
  # Count cells in an sce file
  # Args:
  # - sce_file: path to the SingleCellExperiment file
  # Returns a data frame with the following columns:
  # - project_id
  # - sample_id
  # - library_id
  # - n_cells: number of cells in the library

@@

## Session info
